---
title: "Weekly Report"
output:
  html_document:
    fig_caption: no
    theme: paper
  pdf_document: default
---

<style type="text/css">
h2 {
    text-align: left;
}

body {
    text-align: center;
}

.columnize {
    column-count: 2;
    -moz-column-count: 2;
    -webkit-column-count: 2;
}

.columnize img {
    width: 75%;
    height: auto;
}

.summary {
    text-align: left;
}

.graph {
    text-align: center;
}
</style>


```{r, echo=F}
library(dplyr, warn.conflicts = F)
library(ggplot2)
library(jsonlite, quietly = T)
library(rmarkdown)
options(digits.sec = 3)

convert_date <- function(n) {
    as.POSIXct(n / 1000, origin = "1970-01-01")
}

msToHrs <- function(n) {
    n / 1000 / 60 / 60
}

Time <- function(ms, ...) {
    strftime(as.POSIXct(ms / 1000, tz = "GMT", ...), "%H.%M", tz = "GMT")
}

ordered_days <- weekdays(seq.Date(from = Sys.Date() - 6, to = Sys.Date(), by = 1), 
                         abbreviate = F)
dates.df <- data_frame(date = factor(ordered_days,ordered_days))

l <- fromJSON(readLines("~/Dropbox/share/actionis-log_v2.json"))
l$queue <- NULL

data.df <- lapply(1:length(l), function(i) {
    mutate(l[[i]], date = as.numeric(names(l)[i]) %>% convert_date %>% as.Date(., tz = ""),
                   duration = msToHrs(duration) %>% signif(digits = 3))
}) %>% 
    bind_rows %>% 
    filter((Sys.Date() - 7) < date & date <= Sys.Date()) %>%
    mutate(start = Time(start, origin = date),
           stop = Time(stop, origin = date),
           date = factor(weekdays(date, F), ordered_days)) %>%
    full_join(dates.df, by = "date") %>%
    mutate(duration = ifelse(is.na(duration), 0, duration)) %>%
    select(-timestamp)

tags <- unlist(data.df$tags) %>% unique
hrs <- sum(data.df$duration)
total_hrs <- nrow(data.df) * 15
```

## Top Entries

```{r, echo=F}
library(pander)
na.omit(data.df) %>%
    arrange(desc(duration)) %>%
    pander(style = "rmarkdown")
```

## Top Tags

```{r, echo=F}
# This is embarrasing
tags.df <- data.df %>% 
    rowwise() %>% 
    do({
        tags <- unlist(.$tags)
        len <- ifelse(is.null(tags), 1, length(tags))
        lapply(1:len, function(i) {
            l <- rep(.)
            l$tags <- tags[i]
            l
        }) %>% bind_rows
    }) %>% 
    ungroup %>%
    rename(tag = tags) %>%
    na.omit

comb.df <- expand.grid(tag = unique(tags.df$tag), date = ordered_days)
tags.df <- mutate(comb.df, tag = as.character(tag)) %>%
    full_join(tags.df, by = c("tag", "date")) %>%
    mutate(duration = ifelse(is.na(duration), 0, duration),
           date = factor(date, ordered_days))

ggplot(tags.df, aes(date, duration, group = tag, color = factor(tag))) +
    geom_point() + geom_line() + ylim(0, 16) + coord_fixed(ratio = 0.2) +
    ggtitle("Tracked Duration by Tag") + theme(axis.title = element_blank())
```

### Total

<div class="columnize">
```{r echo=F}
tags_totals.df <- group_by(tags.df, tag) %>%
    summarise(total = sum(duration)) %>%
    arrange(desc(total))

ggplot(tags_totals.df, aes("", total, fill = tag)) + 
    geom_bar(width = 1, stat = "identity") + 
    coord_polar("y") +
    theme(panel.background = element_rect(fill = "transparent", color = NA),
          legend.title = element_blank(), 
          legend.text = element_text(size = 20), axis.title = element_blank(),
          axis.text = element_blank(), axis.ticks = element_blank())
```

`r pander(tail(tags_totals.df, 5))`
</div>

## Summary { .summary }

    - Activities: `r nrow(data.df)`
    - Tags: `r sapply(data.df$tags, length) %>% sum`
    - Hours Logged: `r hrs`/`r total_hrs`
    - Coverage: `r signif(hrs / total_hrs * 100, digits=4)`%

<div class="graph">
```{r, echo=F}
ggplot(data = data.df, aes(date, duration)) + 
    ggtitle("Hours Logged") + theme(axis.title = element_blank()) +
    geom_bar(stat = "identity", show.legend = F) + 
    ylim(0, 16)
```
</div>
